{\bf Demystifying Debugging}

### 2012-11-06 gpi-debug/debugging.tex
tell a story of space and conclusions

\begin{frame}{Outline}
	\textbf{Why teach debugging?}
		% brief motivation
		% toolbox
	\linegap

@@

	{\bf Assorted Tricks}
	\begin{itemize}
		\item Question assumptions
		\item Collect data
	\end{itemize}
\end{frame}

@@

\breakslide{{\bf When} things go wrong\dots}

@@

	\linegap
	\includegraphics[width=\textwidth]{time0.png}
\end{frame}

@@

	\linegap
		\texttt{~~~~\hilight{brown}{foreach}~element~\hilight{brown}{in}~input~\{} \\
		\texttt{~~~~~~~~\hilight{olivegreen}{print(output);}} \\
		\texttt{~~~~~~~~insert\_sorted(output,~element);} \\
		\texttt{~~~~\}} \\
\end{frame}

@@

	\linegap
	\includegraphics[width=\textwidth]{time1.png}
\end{frame}

\begin{frame}{Asserts: Stealthier, more concealable prints}
\end{frame}

@@

\breakslide{{\bf Where} things go wrong\dots}

@@

	\linegap
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Main Approach}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{frame}{Outline}
	\begin{columns}[l]
	\column{0.05\textwidth}
	\column{0.5\textwidth}
	\textbf{Why teach debugging?}
		% brief motivation
		% toolbox
	\linegap

@@

	{\bf Assorted Tricks}
	\begin{itemize}
		\item Question assumptions
		\item Collect data
	\end{itemize}
	\column{0.45\textwidth}
	%\begin{center}
	%	\includegraphics[width=0.9\textwidth]{vip1066720.jpg}
	%\end{center}
	\end{columns}
\end{frame}

@@

\breakslide{``Time Travel'': {\bf When} things go wrong\dots}

@@

	\includegraphics[width=\textwidth]{time0.png}
\end{frame}

@@

	\linegap
		\texttt{~~~~\hilight{brown}{foreach}~element~\hilight{brown}{in}~input~\{} \\
		\texttt{~~~~~~~~\hilight{olivegreen}{print(output);}} \\
		\texttt{~~~~~~~~insert\_sorted(output,~element);} \\
		\texttt{~~~~\}} \\
	\pause
	\linegap

	Creating {\em bounds} on when the problem happened
	\begin{itemize}
		\item Adding more prints = making bounds smaller
		\item (Lots and lots of time? Binary search!)
	\end{itemize}
\end{frame}

@@

	\includegraphics[width=\textwidth]{time1.png}
\end{frame}

\begin{frame}{Asserts: Stealthier, more concealable prints}
	Adding print statements everywhere is very verbose
	\begin{itemize}
		\item Pro: Get to see everything
		\item Con: Have to look at everything
	\end{itemize}
	\pause
	\linegap

	% TODO
\end{frame}

@@

\breakslide{``Space Travel'': {\bf Where} things go wrong\dots}

@@

	\linegap
	{\em Space-wise}, this means ``It supports doing X and Y operations, but operation Z is broken.''
	\begin{itemize}
		\item Now you can ignore X and Y
	\end{itemize}
\end{frame}

\begin{frame}{Minimizing the Test Case}
	Our test case tells this story:

	\begin{center}
	\includegraphics[width=0.65\textwidth]{space0.png}
	\end{center}
\end{frame}

\begin{frame}{Minimizing the Test Case}
	Which parts of your code are right?
	\begin{itemize}
		\item Write {\bf small tests that pass}
	\end{itemize}
	\linegap

	Which parts of your code are wrong?
	\begin{itemize}
		\item {\bf Minimize the failing test}
		\begin{itemize}
			\item Make it as small as possible, such that it still fails
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

	\texttt{~~~~input~=~\hilight{brickred}{[99]};~~~~~\hilight{darkcyan}{//~OK}} \\
	\texttt{~~~~input~=~\hilight{brickred}{[100,99]};~\hilight{darkcyan}{//~OK}} \\
	\pause
	\texttt{~~~~input~=~\hilight{brickred}{[99,100]};~\hilight{darkcyan}{//~Fails}} \\
\end{frame}

\begin{frame}{Minimizing the Test Case}
	New story:

	\begin{center}
	\includegraphics[width=0.65\textwidth]{space1.png}
	\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Assorted Tricks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\breakslide{Assorted Tricks \\ {\normalsize (Useful stuff that isn't really about ``space'' or ``time'')}}

% TODO
%\begin{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\breakslide{What's in this ``toolbox'', again? \\ {\normalsize (Conclusion)}}

\begin{frame}{The Toolbox}
	\begin{columns}[l]
	\column{0.05\textwidth}
	\column{0.5\textwidth}
	\textbf{``Tell Me a Story''}
	\begin{itemize}
		\item Get more detail
		\item Rinse \& repeat
		\pause
		\item {\bf Tell a Story of Time}
		\begin{itemize}
			\item Print debugging
			\item Asserts
		\end{itemize}
		\pause
		\item {\bf Tell a Story of Space}
		\begin{itemize}
			\item Minimize the failing test case
			\item Make small tests that work
		\end{itemize}
		\pause
		\item Draw pictures, collect data, question assumptions
	\end{itemize}
	\column{0.45\textwidth}
	\pause
	\begin{center}
		\includegraphics[width=0.9\textwidth]{vip1066720.jpg}
	\end{center}
	\end{columns}
\end{frame}
